More genes from body systems to add to dashboard on various diseases

There are many substances people encounter in their life at various points that we find out can affect long term health like drugs, or over the counter drugs, treating diseases like yeast infections or vaginal dryness or allergies, or using lubricants or condoms. It can't be avoided and no apologies as these topics are out of bounds for most formal conversations, but many people (Concetta R., AQPO Neff, and Danny L., Tina L., Sarah P., Chayla B., Diane R., and others) have used all of the above or know someone who has, or want to see how the body reacts under a list of various illicit drugs according to the top ranked genes. So this added set of genes is for those body systems. It would go against science to exclude some of these informal ingredients but I also wanted to include herbal teas known off the top of my mind, some natural remedy plants, and vegetables and fruits to compare. Think of this as the 'cards against humanity' type of filters to see how the top genes of these systems and networks in the body reactions affect the disease and healthy state of the various tissue samples.

```{r}
source('geneCards2.R')
```

Get all the genes first.
```{r}

# ingredients in Degree deodorant 'shower clean' invisible solid
#Aluminium zirconium tetrachlorohydrex gly ---not in genecards.org
#cyclopentasiloxane  ---not in genecards.org
find25genes('isopropyl palmitate')
find25genes('stearyl alcohol')
find25genes('mineral oil')
find25genes('talc')
find25genes('hydrogenated castor oil')
find25genes('parfum')
find25genes('BHT')
#steareth-100   ---not in genecards.org


find25genes('antipsychotics')
find25genes('anxiety') 
find25genes('depression')
find25genes('turnip greens')
find25genes('mango')
find25genes('garlic')
find25genes('peppers')
find25genes('yeast infection')
find25genes('shingles')
find25genes('herpes simples 1')
find25genes('herpes simplex 2')
find25genes('ghb') #illicit drug
find25genes('kale')
find25genes('miconazole nitrate') #yeast infection active ingredient
find25genes('ginger')
find25genes('green onions')
find25genes('onion')
find25genes('red onions')
find25genes('benadryl')
find25genes('tylenol pm')
find25genes('flavanoids')
find25genes('spermicide') #birth contraceptive
find25genes('rohypnol') #date rape drug
find25genes('echinacea') #herbal remedy
find25genes('st johns wart') #herbal remedy
find25genes('silicone')
find25genes('mushrooms')
find25genes('epstein barr virus')
find25genes('jackfruit')
find25genes('cashews')
find25genes('perfume')
find25genes('latex')
find25genes('green tea')
find25genes('peppercorn') #black pepper
find25genes('ketamine') #illicit drug
find25genes('visine')
find25genes('turmeric')
find25genes('goldenseal') #home remedy herbal
find25genes('claritin') #otc allergy pill
find25genes('matches') #people lost fingers in match factories from sulfur
find25genes('salmon')
find25genes('codeine') #regulated pain killer
find25genes('nicotine') #cigarrette addictive ingredient
find25genes('vicodine') #regulated pain killer
find25genes('heroin') #illicit drug
find25genes('cocaine') #illicit drug
find25genes('tuberculosis') #related to epstein barr virus
find25genes('mononucleosis') #related to epstein barr virus
find25genes('malaria') #next gen gets sickle cell in some cases
find25genes('mineral oil') #ingredient in menopause vaginal inserts
find25genes('psychedelic') #illicit drug
find25genes('mdma') #illicit drug ecstacy or molly
find25genes('opiates') #illicit drug or regulated pain killer
find25genes('methamphetamines') #illicit drug
find25genes('sudafed') #ID for its use in making methamphetamines an illicit drug
find25genes('weed eater') #roundup lawsuit linked to lymphoma
find25genes('weed killer') #roundup lawsuit linked to lymphoma
find25genes('lentils')
find25genes('allegra') #otc allergy pill
find25genes('chocolate')
find25genes('starfruit ')
find25genes('curry')
find25genes('bean sprouts')
find25genes('broccoli sprouts')
find25genes('bay leaves')
find25genes('basil')
find25genes('blackberries')
find25genes('blueberries')
find25genes('arugula')
find25genes('tannins') #linked to coffees and stored or processed meats and cheeses
find25genes('fennel') #super food vegetable
find25genes('beets') #eastern european and southern vegetable
find25genes('soy')
find25genes('yams')
find25genes('sweet potato')
find25genes('cabbage')
find25genes('carrots')
find25genes('vaginal dryness')
find25genes('boc choi')
find25genes('sex lubricant')
find25genes('birth contraceptive')

find25genes('xanax') 
#anxiety prescribed medicine that people have suicidal withdrawals from

find25genes('celery')
find25genes('acetylcholine')
find25genes('broccoli')
find25genes('epinephrine') #fight or flight chemical by adrenals
find25genes('norepinephrine') #fight or flight chemical by adrenals
find25genes('chamomile') #herbal tea
find25genes('antihistamine')
find25genes('jasmine') #herbal tea
find25genes('yerba mate') #alternate to caffeine or used with caffeine
find25genes('gingko biloba') #similar to yerba mate
find25genes('ginseng')
find25genes('syphilis')
find25genes('gonorrhea')
find25genes('chlamydia')

find25genes('baby powder')
#linked to ovarian cancer as a chemical can be absorbed and cause tumors

find25genes('candles')
find25genes('incontinence') #trouble holding bladder or bowels from trauma or age

#replens ingredients from a vaginal dryness product
find25genes('polycarbophil')
find25genes('mineral oil')
find25genes('hydrogenated palm oil glyceride')

#alternate name for carbomer homopolymer type B
find25genes('allyl pentaerythritol crosslinked')

find25genes('glycerine')

find25genes('grapefruit')
find25genes('strawberries')
find25genes('maple syrup')
find25genes('corn')
find25genes('lime')
find25genes('lemon')
find25genes('cranberries')
find25genes('cherries')
find25genes('plums')
find25genes('figs')
find25genes('dates')
find25genes('squash')
find25genes('zucchini')
find25genes('egg plant')
find25genes('Orange')
find25genes('bananas')
find25genes('almonds')
find25genes('oregano')
find25genes('red fennel')
find25genes('peas')
find25genes('beans')
find25genes('pineapple')
find25genes('cantelope')
find25genes('watermelon')
find25genes('peanuts')
find25genes('hazelnuts')
find25genes('pine nuts')
find25genes('pumpkin')
find25genes('walnuts')
find25genes('chestnuts')
find25genes('coconut')
find25genes('sunflower seeds')
find25genes('pistachio')
find25genes('macadamia nuts')
find25genes('corn nuts')
find25genes('pecans')
find25genes('brazil nuts')
find25genes('okra')
find25genes('green beans')
find25genes('black eyed Peas')
find25genes('sesame seeds')
find25genes('caraway')
find25genes('papaya')
find25genes('papaya seeds')
find25genes('anise') #herb tastes/smells like black licorice
find25genes('gelatin')


#ingredients in tampons
find25genes('cotton')
find25genes('rayon')
find25genes('polyester')
find25genes('polypropylene')
find25genes('polyethylene')

#online listed ingredients of astroglide
find25genes('glycerine')
find25genes('hydroxyethyl cellulose')
find25genes('chlorhexidine gluconate')
find25genes('methylparaben')
find25genes('gluconolactene')
find25genes('sodium hydroxide')

#online listed ingredients of astroglide
find25genes('propylene-glycol')
find25genes('peg-8')
find25genes('hydroxypropylcellulose')


#online listed banned ingredient in jack3d pre-workout
find25genes('DMAA')

#online listed jack3d pre-workout not banned
find25genes('beta alanine')
find25genes('monohydrate')
find25genes('nitric oxide')
find25genes('adaptogen blend')
find25genes('yohimbe')
find25genes('schisandra chinensis')

#protein powder ingredients body fortress
find25genes('betaine anhydrous')
find25genes('milk protein isolate')
find25genes('whey protein isolate')
find25genes('soy lecithin')
find25genes('carrageenan')
find25genes('dextrin')
find25genes('acesulfame potassium')
find25genes('sucralose')

#preworkout ingredients in SixStar brand We already have in our dataset from
#ulcerative colitis and crohn's disease study
# find25genes('choline bitartrate')
# find25genes('L-arginine alpha-ketoglutarate')
# find25genes('L-citruline')
# find25genes('L-arginine hydrochloride')
# find25genes('caffeine anhydrous')
# find25genes('L-tyrosine')
# find25genes('L-carnitine L-tartrate')
# find25genes('green coffee extract')
# find25genes('silicon dioxide')
# find25genes('malic acid')
# find25genes('sucralose')
# find25genes('FD&C Red No. 40')
# find25genes('acesulfame-potassium')


#personal lubricants
#listed online ingredients in astroglide
find25genes('glycerine')
find25genes('hydroxyethyl cellulose')
find25genes('chlorhexidine gluconate')
find25genes('methylparaben')
find25genes('gluconolactone')
find25genes('sodium hydroxide')

#listed online ingredients in K-y warming lubricant
find25genes('propylene-glycol')
find25genes('peg-8')
find25genes('hydroxypropylcellulose')

find25genes('gun powder')
find25genes('tear gas')
find25genes('crying')
find25genes('pepper spray')
find25genes('neuroma')
find25genes('fibromyalgia')
find25genes('eucalyptus')
find25genes('bug spray')
find25genes('rosemary')
#lavendar, lavender, lavandula not listed on genecards.org

#off! bug repellant ingredients
find25genes('deet')
find25genes('butane')
find25genes('propane')
find25genes('isobutane')
find25genes('ethanol')
find25genes('corn starch')
find25genes('magnesium carbonate')
find25genes('isopropyl myristate')
find25genes('aminomethyl propanol')
#dimethicone not listed on genecards.org
find25genes('sodium benzoate')

find25genes('anesthesia')
find25genes('intra uterine device')

find25genes('polyurethane') #alternative to latex birth control
find25genes('demerol') #opioid pain medicine


```



```{r}

getProteinGenes('isopropyl palmitate')
getProteinGenes('stearyl alcohol')
getProteinGenes('mineral oil')
getProteinGenes('talc')
getProteinGenes('hydrogenated castor oil')
getProteinGenes('parfum')
getProteinGenes('BHT')
getProteinGenes('antipsychotics')
getProteinGenes('anxiety') 
getProteinGenes('depression')
getProteinGenes('turnip greens')
getProteinGenes('mango')
getProteinGenes('garlic')
getProteinGenes('peppers')
getProteinGenes('yeast infection')
```

```{r}
isopropylPalmitate <- read.csv("Top25isopropyl-palmitates.csv")
stearylAlcohol <- read.csv("Top25stearyl-alcohols.csv")
mineralOil <- read.csv("Top25mineral-oils.csv")
talc <- read.csv("Top25talcs.csv")
hydrogenatedCastorOil <- read.csv("Top25hydrogenated-castor-oils.csv")
parfum <- read.csv("Top25parfums.csv")
bht <- read.csv("Top25bhts.csv")
antipsychotics <- read.csv("Top25antipsychoticss.csv")
anxiety <- read.csv("Top25anxietys.csv")
depression <- read.csv("Top25depressions.csv")
turnipGreens <- read.csv("Top25turnip-greenss.csv")
mango <- read.csv("Top25mangos.csv")
garlic <- read.csv("Top25garlics.csv")
peppers <- read.csv("Top25pepperss.csv")
yeastInfection <- read.csv("Top25yeast-infections.csv")

```


```{r}
getProteinGenes('shingles')
getProteinGenes('herpes simples 1')
getProteinGenes('herpes simplex 2')
getProteinGenes('ghb') 
getProteinGenes('kale')
getProteinGenes('miconazole nitrate') 
getProteinGenes('ginger')
getProteinGenes('green onions')
getProteinGenes('onion')
getProteinGenes('red onions')
getProteinGenes('benadryl')
getProteinGenes('tylenol pm')
getProteinGenes('flavanoids')
getProteinGenes('spermicide') 
getProteinGenes('rohypnol') 
```


```{r}
shingles <- read.csv("Top25shingless.csv")
herpes1 <- read.csv("Top25herpes-simples-1s.csv")
herpes2 <- read.csv("Top25herpes-simplex-2s.csv")
ghb <- read.csv("Top25ghbs.csv")
kale <- read.csv("Top25kales.csv")
miconazoleNitrate <- read.csv("Top25miconazole-nitrates.csv")
ginger <- read.csv("Top25gingers.csv")
greenOnions <- read.csv("Top25green-onionss.csv")
onions <- read.csv("Top25onions.csv")
redOnions <- read.csv("Top25red-onionss.csv")
benadryl <- read.csv("Top25benadryls.csv")
tylenolPM <- read.csv("Top25tylenol-pms.csv")
flavanoids <- read.csv("Top25flavanoidss.csv")
spermicide <- read.csv("Top25spermicides.csv")
rohypnol <- read.csv("Top25rohypnols.csv")

```



```{r}
getProteinGenes('echinacea') 
getProteinGenes('st johns wart') 
getProteinGenes('silicone')
getProteinGenes('mushrooms')
getProteinGenes('epstein barr virus')
getProteinGenes('jackfruit')
getProteinGenes('cashews')
getProteinGenes('perfume')
getProteinGenes('latex')
getProteinGenes('green tea')
getProteinGenes('peppercorn') 
getProteinGenes('ketamine') 
getProteinGenes('visine')
getProteinGenes('turmeric')
getProteinGenes('goldenseal')
```


```{r}
echinacea <- read.csv("Top25echinaceas.csv")
stJohnsWart <- read.csv("Top25st-johns-warts.csv")
silicone <- read.csv("Top25silicones.csv")
mushrooms <- read.csv("Top25mushroomss.csv")
epsteinBarr <- read.csv("Top25epstein-barr-viruss.csv")
jackfruit <- read.csv("Top25jackfruits.csv")
cashews <- read.csv("Top25cashewss.csv")
perfume <- read.csv("Top25perfumes.csv")
latex <- read.csv("Top25latexs.csv")
greenTea <- read.csv("Top25green-teas.csv")
peppercorn <- read.csv("Top25peppercorns.csv")
ketamine <- read.csv("Top25ketamines.csv")
visine <- read.csv("Top25visines.csv")
turmeric <- read.csv("Top25turmerics.csv")
goldenseal <- read.csv("Top25goldenseals.csv")
```



```{r}
getProteinGenes('claritin') 
getProteinGenes('matches') 
getProteinGenes('salmon')
getProteinGenes('codeine') 
getProteinGenes('nicotine')
getProteinGenes('vicodine') 
getProteinGenes('heroin') 
getProteinGenes('cocaine') 
getProteinGenes('tuberculosis') 
getProteinGenes('mononucleosis') 
getProteinGenes('malaria') 
getProteinGenes('psychedelic') 
getProteinGenes('mdma') 
getProteinGenes('opiates')
```


```{r}
claritin <- read.csv("Top25claritins.csv")
matches <- read.csv("Top25matchess.csv")
salmon <- read.csv("Top25salmons.csv")
codeine <- read.csv("Top25codeines.csv")
nicotine <- read.csv("Top25nicotines.csv")
vicodine <- read.csv("Top25vicodines.csv")
heroin <- read.csv("Top25heroins.csv")
cocaine <- read.csv("Top25cocaines.csv")
tuberculosis <- read.csv("Top25tuberculosiss.csv")
mononucleosis <- read.csv("Top25mononucleosiss.csv")
malaria <- read.csv("Top25malarias.csv")
psychedelic <- read.csv("Top25psychedelics.csv")
mdma <- read.csv("Top25mdmas.csv")
opiates <- read.csv("Top25opiatess.csv")
```



```{r}
getProteinGenes('methamphetamines') 
getProteinGenes('sudafed') 
getProteinGenes('weed eater') 
getProteinGenes('weed killer') 
getProteinGenes('lentils')
getProteinGenes('allegra') 
getProteinGenes('egg plant')
getProteinGenes('chocolate')
getProteinGenes('starfruit ')
getProteinGenes('curry')
getProteinGenes('bean sprouts')
getProteinGenes('broccoli sprouts')
getProteinGenes('bay leaves')
getProteinGenes('basil')
getProteinGenes('blackberries')
```


```{r}
meth <- read.csv("Top25methamphetaminess.csv")
sudafed <- read.csv("Top25sudafeds.csv")
weedEater <- read.csv("Top25weed-eaters.csv")
weedKiller <- read.csv("Top25weed-killers.csv")
lentils <- read.csv("Top25lentilss.csv")
allegra <- read.csv("Top25allegras.csv")
eggPlant <- read.csv("Top25egg-plants.csv")
chocolate <- read.csv("Top25chocolates.csv")
starFruit <- read.csv("Top25starfruit-s.csv")
curry <- read.csv("Top25currys.csv")
beanSprouts <- read.csv("Top25bean-sproutss.csv")
broccoliSprouts <- read.csv("Top25broccoli-sproutss.csv")
bayLeaves <- read.csv("Top25bay-leavess.csv")
basil <- read.csv("Top25basils.csv")
blackberries <- read.csv("Top25blackberriess.csv")

```



```{r}
getProteinGenes('blueberries')
getProteinGenes('arugula')
getProteinGenes('tannins') 
getProteinGenes('fennel') 
getProteinGenes('beets') 
getProteinGenes('soy')
getProteinGenes('yams')
getProteinGenes('sweet potato')
getProteinGenes('cabbage')
getProteinGenes('carrots')
getProteinGenes('vaginal dryness')
getProteinGenes('boc choi')
getProteinGenes('sex lubricant')
getProteinGenes('birth contraceptive')
getProteinGenes('xanax') 
```


```{r}
blueberries <- read.csv("Top25blueberriess.csv") 
arugula <- read.csv("Top25arugulas.csv") 
tannins <- read.csv("Top25tanninss.csv") 
fennel <- read.csv("Top25fennels.csv") 
beets <- read.csv("Top25beetss.csv") 
soy <- read.csv("Top25soys.csv") 
yams <- read.csv("Top25yamss.csv") 
sweetPotato <- read.csv("Top25sweet-potatos.csv") 
cabbage <- read.csv("Top25cabbages.csv") 
carrots <- read.csv("Top25carrotss.csv") 
vaginalDryness <- read.csv("Top25vaginal-drynesss.csv") 
bocChoi <- read.csv("Top25boc-chois.csv") 
sexLubricant <- read.csv("Top25sex-lubricants.csv") 
birthContraceptive <- read.csv("Top25birth-contraceptives.csv") 
xanax <- read.csv("Top25xanaxs.csv") 

```



```{r}
getProteinGenes('celery')
getProteinGenes('acetylcholine')
getProteinGenes('broccoli')
getProteinGenes('epinephrine') 
getProteinGenes('norepinephrine') 
getProteinGenes('chamomile') 
getProteinGenes('antihistamine')
getProteinGenes('jasmine') 
getProteinGenes('yerba mate') 
getProteinGenes('gingko biloba') 
getProteinGenes('ginseng')
getProteinGenes('syphilis')
getProteinGenes('gonorrhea')
getProteinGenes('chlamydia')
getProteinGenes('baby powder')
```


```{r}
celery <- read.csv("Top25celerys.csv") 
acetylcholine <- read.csv("Top25acetylcholines.csv") 
broccoli <- read.csv("Top25broccolis.csv") 
epinephrine <- read.csv("Top25epinephrines.csv") 
norepinephrine <- read.csv("Top25norepinephrines.csv") 
chamomile <- read.csv("Top25chamomiles.csv") 
antihistamine <- read.csv("Top25antihistamines.csv") 
jasmine <- read.csv("Top25jasmines.csv") 
yerbaMate <- read.csv("Top25yerba-mates.csv") 
gingkoBiloba <- read.csv("Top25gingko-bilobas.csv") 
ginseng <- read.csv("Top25ginsengs.csv") 
syphilis <- read.csv("Top25syphiliss.csv") 
gonorrhea <- read.csv("Top25gonorrheas.csv") 
chlamydia <- read.csv("Top25chlamydias.csv") 
babyPowder <- read.csv("Top25baby-powders.csv") 

```




```{r}
getProteinGenes('candles')
getProteinGenes('incontinence') 
getProteinGenes('polycarbophil')
getProteinGenes('hydrogenated palm oil glyceride')
getProteinGenes('allyl pentaerythritol crosslinked')
getProteinGenes('glycerine')
getProteinGenes('grapefruit')
getProteinGenes('strawberries')
getProteinGenes('maple syrup')
getProteinGenes('corn')
getProteinGenes('lime')
getProteinGenes('lemon')
getProteinGenes('cranberries')
getProteinGenes('cherries')
```


```{r}
candles <- read.csv("Top25candless.csv") 
incontinence <- read.csv("Top25incontinences.csv") 
polycarbophil <- read.csv("Top25polycarbophils.csv") 
hydrogenatedPalmOilGlyceride <- read.csv("Top25hydrogenated-palm-oil-glycerides.csv")
allylPentaerythritolCrosslinked <- read.csv("Top25allyl-pentaerythritol-crosslinkeds.csv") 
glycerine <- read.csv("Top25glycerines.csv") 
grapefruit <- read.csv("Top25grapefruits.csv") 
strawberries <- read.csv("Top25strawberriess.csv") 
mapleSyrup <- read.csv("Top25maple-syrups.csv") 
corn <- read.csv("Top25corns.csv") 
lime <- read.csv("Top25limes.csv") 
lemon <- read.csv("Top25lemons.csv") 
cranberries <- read.csv("Top25cranberriess.csv") 
cherries <- read.csv("Top25cherriess.csv") 

```



```{r}
getProteinGenes('plums')
getProteinGenes('figs')
getProteinGenes('dates')
getProteinGenes('squash')
getProteinGenes('zucchini')
getProteinGenes('Orange')
getProteinGenes('bananas')
getProteinGenes('almonds')
getProteinGenes('oregano')
getProteinGenes('red fennel')
getProteinGenes('peas')
getProteinGenes('beans')
getProteinGenes('pineapple')
getProteinGenes('watermelon')
getProteinGenes('peanuts')
```



```{r}
plums <- read.csv("Top25plumss.csv") 
figs <- read.csv("Top25figss.csv") 
dates <- read.csv("Top25datess.csv") 
squash <- read.csv("Top25squashs.csv") 
zucchini <- read.csv("Top25zucchinis.csv") 
orange <- read.csv("Top25oranges.csv") 
bananas <- read.csv("Top25bananass.csv") 
almonds <- read.csv("Top25almondss.csv") 
oregano <- read.csv("Top25oreganos.csv") 
redFennel <- read.csv("Top25red-fennels.csv") 
peas <- read.csv("Top25peass.csv") 
beans <- read.csv("Top25beanss.csv") 
pineapple <- read.csv("Top25pineapples.csv") 
watermelon <- read.csv("Top25watermelons.csv") 
peanuts <- read.csv("Top25peanutss.csv") 


```



```{r}
getProteinGenes('hazelnuts')
getProteinGenes('pine nuts')
getProteinGenes('pumpkin')
getProteinGenes('walnuts')
getProteinGenes('chestnuts')
getProteinGenes('coconut')
getProteinGenes('sunflower seeds')
getProteinGenes('pistachio')
getProteinGenes('macadamia nuts')
getProteinGenes('corn nuts')
getProteinGenes('pecans')
getProteinGenes('brazil nuts')
getProteinGenes('okra')
getProteinGenes('green beans')
getProteinGenes('black eyed Peas')
```


```{r}
hazelnuts <- read.csv("Top25hazelnutss.csv") 
pineNuts <- read.csv("Top25pine-nutss.csv") 
pumpkin <- read.csv("Top25pumpkins.csv") 
walnuts <- read.csv("Top25walnutss.csv") 
chestnuts <- read.csv("Top25chestnutss.csv") 
coconuts <- read.csv("Top25coconuts.csv") 
sunflowerSeeds <- read.csv("Top25sunflower-seedss.csv") 
pistachio <- read.csv("Top25pistachios.csv") 
macadamiaNuts <- read.csv("Top25macadamia-nutss.csv") 
cornNuts <- read.csv("Top25corn-nutss.csv") 
pecans <- read.csv("Top25pecanss.csv") 
brazilNuts <- read.csv("Top25brazil-nutss.csv") 
okra <- read.csv("Top25okras.csv") 
greenBeans <- read.csv("Top25green-beanss.csv") 
blackEyedPeas <- read.csv("Top25black-eyed-peass.csv") 

```




```{r}
getProteinGenes('sesame seeds')
getProteinGenes('caraway')
getProteinGenes('papaya')
getProteinGenes('papaya seeds')
getProteinGenes('anise') 
getProteinGenes('gelatin')
getProteinGenes('cotton')
getProteinGenes('rayon')
getProteinGenes('polyester')
getProteinGenes('polypropylene')
getProteinGenes('polyethylene')
getProteinGenes('glycerine')
getProteinGenes('hydroxyethyl cellulose')
getProteinGenes('chlorhexidine gluconate')
getProteinGenes('methylparaben')
```


```{r}
sesameSeeds <- read.csv("Top25sesame-seedss.csv") 
caraway <- read.csv("Top25caraways.csv") 
papaya <- read.csv("Top25papayas.csv") 
papayaSeeds <- read.csv("Top25papaya-seedss.csv") 
anise <- read.csv("Top25anises.csv") 
gelatin <- read.csv("Top25gelatins.csv") 
cotton <- read.csv("Top25cottons.csv") 
rayon <- read.csv("Top25rayons.csv") 
polyester <- read.csv("Top25polyesters.csv") 
polypropylene <- read.csv("Top25polypropylenes.csv") 
polyethylene <- read.csv("Top25polyethylenes.csv") 
glycerine <- read.csv("Top25glycerines.csv") 
hydroxyethylCellulose <- read.csv("Top25hydroxyethyl-celluloses.csv") 
chlorhexidineGluconate <- read.csv("Top25chlorhexidine-gluconates.csv") 
methylparaben <- read.csv("Top25methylparabens.csv") 

```



```{r}
getProteinGenes('gluconolactone')
getProteinGenes('sodium hydroxide')
getProteinGenes('propylene-glycol')
getProteinGenes('peg-8')
getProteinGenes('hydroxypropylcellulose')
getProteinGenes('DMAA')
getProteinGenes('beta alanine')
getProteinGenes('monohydrate')
getProteinGenes('nitric oxide')
getProteinGenes('adaptogen blend')
getProteinGenes('yohimbe')
getProteinGenes('schisandra chinensis')
getProteinGenes('betaine anhydrous')
getProteinGenes('milk protein isolate')
getProteinGenes('whey protein isolate')
```


```{r}
gluconolactone <- read.csv("Top25gluconolactones.csv") 
sodiumHydroxide <- read.csv("Top25sodium-hydroxides.csv") 
propyleneGlycol <- read.csv("Top25propylene-glycols.csv") 
peg8 <- read.csv("Top25peg-8s.csv") 
hydroxypropylCellulose <- read.csv("Top25hydroxypropylcelluloses.csv") 
dmaa <- read.csv("Top25dmaas.csv") 
betaAlanine <- read.csv("Top25beta-alanines.csv") 
monohydrate <- read.csv("Top25monohydrates.csv") 
nitricOxide <- read.csv("Top25nitric-oxides.csv") 
adaptogenBlend <- read.csv("Top25adaptogen-blends.csv") 
yohimbe <- read.csv("Top25yohimbes.csv") 
schisandraChinensis <- read.csv("Top25schisandra-chinensiss.csv") 
betaineAnhydrous <- read.csv("Top25betaine-anhydrouss.csv") 
milkProteinIsolate <- read.csv("Top25milk-protein-isolates.csv") 
wheyProteinIsolate <- read.csv("Top25whey-protein-isolates.csv") 

```



```{r}
getProteinGenes('soy lecithin')
getProteinGenes('carrageenan')
getProteinGenes('dextrin')
getProteinGenes('acesulfame potassium')
getProteinGenes('sucralose')
getProteinGenes('glycerine')
getProteinGenes('hydroxyethyl cellulose')
getProteinGenes('chlorhexidine gluconate')
getProteinGenes('methylparaben')
getProteinGenes('gluconolactone')
getProteinGenes('sodium hydroxide')
getProteinGenes('propylene-glycol')
getProteinGenes('peg-8')
getProteinGenes('hydroxypropylcellulose')
getProteinGenes('gun powder')
```


```{r}
soyLecithin <- read.csv("Top25soy-lecithins.csv") 
carrageenan <- read.csv("Top25carrageenans.csv") 
dextrin <- read.csv("Top25dextrins.csv") 
acesulfamePotassium <- read.csv("Top25acesulfame-potassiums.csv") 
sucralose <- read.csv("Top25sucraloses.csv") 
gluconolactone <- read.csv("Top25gluconolactones.csv")
sodiumHydroxide <- read.csv("Top25sodium-hydroxides.csv")
propyleneGlycol <- read.csv("Top25propylene-glycols.csv")
gunPowder <- read.csv("Top25gun-powders.csv") 

```



```{r}
getProteinGenes('tear gas')
getProteinGenes('crying')
getProteinGenes('pepper spray')
getProteinGenes('neuroma')
getProteinGenes('fibromyalgia')
getProteinGenes('eucalyptus')
getProteinGenes('bug spray')
getProteinGenes('rosemary')
getProteinGenes('deet')
getProteinGenes('butane')
getProteinGenes('propane')
getProteinGenes('isobutane')
getProteinGenes('ethanol')
getProteinGenes('corn starch')
getProteinGenes('magnesium carbonate')
```


```{r}
tearGas <- read.csv("Top25tear-gass.csv") 
crying <- read.csv("Top25cryings.csv") 
pepperSpray <- read.csv("Top25pepper-sprays.csv") 
neuroma <- read.csv("Top25neuromas.csv") 
fibromyalgia <- read.csv("Top25fibromyalgias.csv") 
eucalyptus <- read.csv("Top25eucalyptuss.csv") 
bugSpray <- read.csv("Top25bug-sprays.csv") 
rosemary <- read.csv("Top25rosemarys.csv") 
deet <- read.csv("Top25deets.csv") 
butane <- read.csv("Top25butanes.csv") 
propane <- read.csv("Top25propanes.csv") 
isobutane <- read.csv("Top25isobutanes.csv") 
ethanol <- read.csv("Top25ethanols.csv") 
cornStarch <- read.csv("Top25corn-starchs.csv") 
magnesiumCarbonate <- read.csv("Top25magnesium-carbonates.csv") 

```




```{r}
getProteinGenes('isopropyl myristate')
getProteinGenes('aminomethyl propanol')
getProteinGenes('sodium benzoate')
getProteinGenes('anesthesia')
getProteinGenes('intra uterine device')
getProteinGenes('polyurethane') 
getProteinGenes('demerol') 

```

```{r}
isopropylMyristate <- read.csv("Top25isopropyl-myristates.csv") 
aminomethylPropanol <- read.csv("Top25aminomethyl-propanols.csv") 
sodiumBenzoate <- read.csv("Top25sodium-benzoates.csv") 
anesthesia <- read.csv("Top25anesthesias.csv") 
iud <- read.csv("Top25intra-uterine-devices.csv") 
polyurethane <- read.csv("Top25polyurethanes.csv") 
demerol <- read.csv("Top25demerols.csv") 

```


```{r}
for (i in zucchini$proteinType[1:5]){
  getSummaries2(i,'zucchini')
}

for (i in yohimbe$proteinType[1:5]){
  getSummaries2(i,'yohimbe')
}

for (i in yerbaMate$proteinType[1:3]){
  getSummaries2(i,'yerba mate')
}

for (i in yeastInfection$proteinType[1:5]){
  getSummaries2(i,'yeast infection')
}

for (i in yams$proteinType[1:5]){
  getSummaries2(i,'yams')
}

for (i in xanax$proteinType[1:5]){
  getSummaries2(i,'xanax')
}

for (i in wheyProteinIsolate$proteinType[1:5]){
  getSummaries2(i,'whey protein isolate')
}

for (i in weedKiller$proteinType[1:5]){
  getSummaries2(i,'weed killer')
}

for (i in weedEater$proteinType[1]){
  getSummaries2(i,'weed eater')
}

for (i in watermelon$proteinType[1:5]){
  getSummaries2(i,'watermelon')
}

for (i in walnuts$proteinType[1:5]){
  getSummaries2(i,'walnuts')
}

for (i in visine$proteinType[1:5]){
  getSummaries2(i,'visine')
}

for (i in vicodine$proteinType[1:5]){
  getSummaries2(i,'vicodine')
}

for (i in vaginalDryness$proteinType[1:5]){
  getSummaries2(i,'vaginal dryness')
}

for (i in tylenolPM$proteinType[1:5]){
  getSummaries2(i,'tylenol PM')
}

for (i in turnipGreens$proteinType[1:5]){
  getSummaries2(i,'turnip greens')
}

for (i in turmeric$proteinType[1:5]){
  getSummaries2(i,'turmeric')
}

for (i in tuberculosis$proteinType[1:5]){
  getSummaries2(i,'tuberculosis')
}

for (i in tearGas$proteinType[1:5]){
  getSummaries2(i,'tear gas')
}

for (i in tannins$proteinType[1:5]){
  getSummaries2(i,'tannins')
}

for (i in talc$proteinType[1:5]){
  getSummaries2(i,'talc')
}

for (i in syphilis$proteinType[1:5]){
  getSummaries2(i,'syphilis')
}

for (i in sweetPotato$proteinType[1:5]){
  getSummaries2(i,'sweet potato')
}

for (i in sunflowerSeeds$proteinType[1:5]){
  getSummaries2(i,'sunflower seeds')
}


```

```{r}
getGeneSummaries('zucchini')
getGeneSummaries('yohimbe')
getGeneSummaries('yerba mate')
getGeneSummaries('yeast infection')
getGeneSummaries('yams')
getGeneSummaries('xanax')
getGeneSummaries('whey protein isolate')
getGeneSummaries('weed killer')
getGeneSummaries('weed eater')
getGeneSummaries('watermelon')
getGeneSummaries('walnuts')
getGeneSummaries('visine')
getGeneSummaries('vicodine')
getGeneSummaries('vaginal dryness')
getGeneSummaries('tylenol pm')
getGeneSummaries('turnip greens')
getGeneSummaries('turmeric')
getGeneSummaries('tuberculosis')
getGeneSummaries('tear gas')
getGeneSummaries('tannins')
getGeneSummaries('talc')
getGeneSummaries('syphilis')
getGeneSummaries('sweet potato')
getGeneSummaries('sunflower seeds')


```

```{r}
sunflowerSeedsSumms <- read.csv("proteinGeneSummaries_sunflower-seeds.csv")
sweetPotatoSumms <- read.csv("proteinGeneSummaries_sweet-potato.csv")
syphilisSumms <- read.csv("proteinGeneSummaries_syphilis.csv")
talcSumms <- read.csv("proteinGeneSummaries_talc.csv")
tanninsSumms <- read.csv("proteinGeneSummaries_tannins.csv")
tearGasSumms <- read.csv("proteinGeneSummaries_tear-gas.csv")
tuberculosisSumms <- read.csv("proteinGeneSummaries_tuberculosis.csv")
turmericSumms <- read.csv("proteinGeneSummaries_turmeric.csv")
turnipGreensSumms <- read.csv("proteinGeneSummaries_turnip-greens.csv")
tylenolPMSumms <- read.csv("proteinGeneSummaries_tylenol-pm.csv")
vaginalDrynessSumms <- read.csv("proteinGeneSummaries_vaginal-dryness.csv")
vicodineSumms <- read.csv("proteinGeneSummaries_vicodine.csv")
visineSumms <- read.csv("proteinGeneSummaries_visine.csv")
walnutsSumms <- read.csv("proteinGeneSummaries_walnuts.csv")
watermelonSumms <- read.csv("proteinGeneSummaries_watermelon.csv")
weedEaterSumms <- read.csv("proteinGeneSummaries_weed-eater.csv")
weedKillerSumms <- read.csv("proteinGeneSummaries_weed-killer.csv")
wheyProteinIsolateSumms <- read.csv("proteinGeneSummaries_whey-protein-isolate.csv")
xanaxSumms <- read.csv("proteinGeneSummaries_xanax.csv")
yamsSumms <- read.csv("proteinGeneSummaries_yams.csv")
yeastInfectionSumms <- read.csv("proteinGeneSummaries_yeast-infection.csv")
yerbaMateSumms <- read.csv("proteinGeneSummaries_yerba-mate.csv")
yohimbeSumms <- read.csv("proteinGeneSummaries_yohimbe.csv")
zucchiniSumms <- read.csv("proteinGeneSummaries_zucchini.csv")

```


```{r}
for (i in sudafed$proteinType[1:5]){
  getSummaries2(i,'sudafed')
}

for (i in sucralose$proteinType[1:5]){
  getSummaries2(i,'sucralose')
}

for (i in strawberries$proteinType[1:5]){
  getSummaries2(i,'strawberries')
}

for (i in stJohnsWart$proteinType[1:5]){
  getSummaries2(i,'st johns wart')
}

for (i in stearylAlcohol$proteinType[1:5]){
  getSummaries2(i,'stearyl alcohol')
}

for (i in starFruit$proteinType[1]){
  getSummaries2(i,'star fruit')
}

for (i in squash$proteinType[1:5]){
  getSummaries2(i,'squash')
}

for (i in spermicide$proteinType[1:5]){
  getSummaries2(i,'spermicide')
}

for (i in soyLecithin$proteinType[1:5]){
  getSummaries2(i,'soy lecithin')
}

for (i in soy$proteinType[1:5]){
  getSummaries2(i,'soy')
}

for (i in sodiumHydroxide$proteinType[1:5]){
  getSummaries2(i,'sodium hydroxide')
}

for (i in sodiumBenzoate$proteinType[1:5]){
  getSummaries2(i,'sodium benzoate')
}

for (i in silicone$proteinType[1:5]){
  getSummaries2(i,'silicone')
}

for (i in shingles$proteinType[1:5]){
  getSummaries2(i,'shingles')
}

for (i in sexLubricant$proteinType[1:5]){
  getSummaries2(i,'sex lubricant')
}

for (i in sesameSeeds$proteinType[1:5]){
  getSummaries2(i,'sesame seeds')
}
```

```{r}
getGeneSummaries('sudafed')
getGeneSummaries('sucralose')
getGeneSummaries('strawberries')
getGeneSummaries('st johns wart')
getGeneSummaries('stearyl alcohol')
getGeneSummaries('star fruit')
getGeneSummaries('squash')
getGeneSummaries('spermicide')
getGeneSummaries('soy lecithin')
getGeneSummaries('soy')
getGeneSummaries('sodium hydroxide')
getGeneSummaries('sodium benzoate')
getGeneSummaries('silicone')
getGeneSummaries('shingles')
getGeneSummaries('sex lubricant')
getGeneSummaries('sudafed')
getGeneSummaries('sudafed')
getGeneSummaries('sesame seeds')

```


```{r}
sudafedSumms <- read.csv("proteinGeneSummaries_sudafed.csv")
sucraloseSumms <- read.csv("proteinGeneSummaries_sucralose.csv")
strawberriesSumms <- read.csv("proteinGeneSummaries_strawberries.csv")
stJohnsWartSumms <- read.csv("proteinGeneSummaries_st-johns-wart.csv")
stearylAlcoholSumms <- read.csv("proteinGeneSummaries_stearyl-alcohol.csv")
starFruitSumms <- read.csv("proteinGeneSummaries_star-fruit.csv")
squashSumms <- read.csv("proteinGeneSummaries_squash.csv")
spermicideSumms <- read.csv("proteinGeneSummaries_spermicide.csv")
soyLecithinSumms <- read.csv("proteinGeneSummaries_soy-lecithin.csv")
soySumms <- read.csv("proteinGeneSummaries_soy.csv")
sodiumHydroxideSumms <- read.csv("proteinGeneSummaries_sodium-hydroxide.csv")
sodiumBenzoateSumms <- read.csv("proteinGeneSummaries_sodium-benzoate.csv")
siliconeSumms <- read.csv("proteinGeneSummaries_silicone.csv")
shinglesSumms <- read.csv("proteinGeneSummaries_shingles.csv")
sexLubricantSumms <- read.csv("proteinGeneSummaries_sex-lubricant.csv")
sesameSeedsSumms <- read.csv("proteinGeneSummaries_sesame-seeds.csv")
```



```{r}
for (i in schisandraChinensis$proteinType[1:5]){
  getSummaries2(i,'schisandra chinensis')
}

for (i in salmon$proteinType[1:5]){
  getSummaries2(i,'salmon')
}

for (i in rosemary$proteinType[1:5]){
  getSummaries2(i,'rosemary')
}

for (i in rohypnol$proteinType[1:5]){
  getSummaries2(i,'rohypnol')
}

for (i in redOnions$proteinType[1:5]){
  getSummaries2(i,'red onions')
}

for (i in redFennel$proteinType[1:5]){
  getSummaries2(i,'red fennel')
}

for (i in rayon$proteinType[1:5]){
  getSummaries2(i,'rayon')
}

for (i in pumpkin$proteinType[1:5]){
  getSummaries2(i,'pumpkin')
}

for (i in psychedelic$proteinType[1:4]){
  getSummaries2(i,'psychedelic')
}

for (i in propyleneGlycol$proteinType[1:5]){
  getSummaries2(i,'propylene glycol')
}

for (i in propane$proteinType[1:5]){
  getSummaries2(i,'propane')
}

for (i in polyurethane$proteinType[1:5]){
  getSummaries2(i,'polyurethane')
}

for (i in polypropylene$proteinType[1:5]){
  getSummaries2(i,'polypropylene')
}

for (i in polyethylene$proteinType[1:5]){
  getSummaries2(i,'polyethylene')
}

for (i in polyester$proteinType[1:5]){
  getSummaries2(i,'polyester')
}

```

```{r}
getGeneSummaries('schisandra chinensis')
getGeneSummaries('salmon')
getGeneSummaries('rosemary')
getGeneSummaries('rohypnol')
getGeneSummaries('red onions')
getGeneSummaries('red fennel')
getGeneSummaries('rayon')
getGeneSummaries('pumpkin')
getGeneSummaries('psychedelic')
getGeneSummaries('propylene glycol')
getGeneSummaries('propane')
getGeneSummaries('polyurethane')
getGeneSummaries('polypropylene')
getGeneSummaries('polyethylene')
getGeneSummaries('polyester')


```

```{r}
polyesterSumms <- read.csv("proteinGeneSummaries_polyester.csv")
polyethyleneSumms <- read.csv("proteinGeneSummaries_polyethylene.csv")
polypropyleneSumms <- read.csv("proteinGeneSummaries_polypropylene.csv")
polyurethaneSumms <- read.csv("proteinGeneSummaries_polyurethane.csv")
propaneSumms <- read.csv("proteinGeneSummaries_propane.csv")
propyleneGlycolSumms <- read.csv("proteinGeneSummaries_propylene-glycol.csv")
psychedelicSumms <- read.csv("proteinGeneSummaries_psychedelic.csv")
pumpkinSumms <- read.csv("proteinGeneSummaries_pumpkin.csv")
rayonSumms <- read.csv("proteinGeneSummaries_rayon.csv")
redFennelSumms <- read.csv("proteinGeneSummaries_red-fennel.csv")
redOnionsSumms <- read.csv("proteinGeneSummaries_red-onions.csv")
rohypnolSumms <- read.csv("proteinGeneSummaries_rohypnol.csv")
rosemarySumms <- read.csv("proteinGeneSummaries_rosemary.csv")
salmonSumms <- read.csv("proteinGeneSummaries_salmon.csv")
schisandraChinensisSumms <- read.csv("proteinGeneSummaries_schisandra-chinensis.csv")


```


```{r}
for (i in polycarbophil$proteinType[1:5]){
  getSummaries2(i,'polycarbophil')
}

for (i in plums$proteinType[1:5]){
  getSummaries2(i,'plums')
}

for (i in pistachio$proteinType[1:5]){
  getSummaries2(i,'pistachio')
}

for (i in pineNuts$proteinType[1:5]){
  getSummaries2(i,'pine nuts')
}

for (i in pineapple$proteinType[1:5]){
  getSummaries2(i,'pineapple')
}

for (i in perfume$proteinType[1:5]){
  getSummaries2(i,'perfume')
}

for (i in pepperSpray$proteinType[1:5]){
  getSummaries2(i,'pepper spray')
}

for (i in peppers$proteinType[1:5]){
  getSummaries2(i,'peppers')
}

for (i in peppercorn$proteinType[1:3]){
  getSummaries2(i,'peppercorn')
}

for (i in peg8$proteinType[1:5]){
  getSummaries2(i,'peg-8')
}

for (i in pecans$proteinType[1:3]){
  getSummaries2(i,'pecans')
}

for (i in peas$proteinType[1:5]){
  getSummaries2(i,'peas')
}

for (i in peanuts$proteinType[1:5]){
  getSummaries2(i,'peanuts')
}

for (i in parfum$proteinType){
  getSummaries2(i,'parfum')
}

for (i in papayaSeeds$proteinType[1:5]){
  getSummaries2(i,'papaya seeds')
}

for (i in papaya$proteinType[1:5]){
  getSummaries2(i,'papaya')
}

```

```{r}
getGeneSummaries('polycarbophil')
getGeneSummaries('plums')
getGeneSummaries('pistachio')
getGeneSummaries('pine nuts')
getGeneSummaries('pineapple')
getGeneSummaries('perfume')
getGeneSummaries('pepper spray')
getGeneSummaries('peppers')
getGeneSummaries('peppercorn')
getGeneSummaries('peg-8')
getGeneSummaries('pecans')
getGeneSummaries('peas')
getGeneSummaries('peanuts')
getGeneSummaries('parfum')
getGeneSummaries('papaya seeds')
getGeneSummaries('papaya')


```

```{r}
polycarbophilSumms <- read.csv("proteinGeneSummaries_polycarbophil.csv")
plumsSumms <- read.csv("proteinGeneSummaries_plums.csv")
pistachioSumms <- read.csv("proteinGeneSummaries_pistachio.csv")
pineNutsSumms <- read.csv("proteinGeneSummaries_pine-nuts.csv")
pineappleSumms <- read.csv("proteinGeneSummaries_pineapple.csv")
perfumeSumms <- read.csv("proteinGeneSummaries_perfume.csv")
pepperSpraySumms <- read.csv("proteinGeneSummaries_pepper-spray.csv")
peppersSumms <- read.csv("proteinGeneSummaries_peppers.csv")
peppercornSumms <- read.csv("proteinGeneSummaries_peppercorn.csv")
peg8Summs <- read.csv("proteinGeneSummaries_peg-8.csv")
pecansSumms <- read.csv("proteinGeneSummaries_pecans.csv")
peasSumms <- read.csv("proteinGeneSummaries_peas.csv")
peanutsSumms <- read.csv("proteinGeneSummaries_peanuts.csv")
parfumSumms <- read.csv("proteinGeneSummaries_parfum.csv")
papayaSeedsSumms <- read.csv("proteinGeneSummaries_papaya-seeds.csv")
papayaSumms <- read.csv("proteinGeneSummaries_papaya.csv")

```


```{r}
for (i in oregano$proteinType[1:4]){
  getSummaries2(i,'oregano')
}

for (i in orange$proteinType[1:5]){
  getSummaries2(i,'orange')
}

for (i in opiates$proteinType[1:5]){
  getSummaries2(i,'opiates')
}

for (i in onions$proteinType[1:5]){
  getSummaries2(i,'onions')
}

for (i in okra$proteinType[1:3]){
  getSummaries2(i,'okra')
}

for (i in norepinephrine$proteinType[1:5]){
  getSummaries2(i,'norepinephrine')
}

for (i in nitricOxide$proteinType[1:5]){
  getSummaries2(i, 'nitric oxide')
}

for (i in nicotine$proteinType[1:5]){
  getSummaries2(i,'nicotine')
}

for (i in neuroma$proteinType[1:5]){
  getSummaries2(i,'neuroma')
}

for (i in mushrooms$proteinType[1:5]){
  getSummaries2(i,'mushrooms')
}

for (i in mononucleosis$proteinType[1:5]){
  getSummaries2(i, 'mononucleosis')
}

for (i in monohydrate$proteinType[1:5]){
  getSummaries2(i,'monohydrate')
}

for (i in mineralOil$proteinType[1:5]){
  getSummaries2(i,'mineral oil')
}

for (i in milkProteinIsolate$proteinType[1:5]){
  getSummaries2(i,'milk protein isolate')
}

for (i in miconazoleNitrate$proteinType[1:5]){
  getSummaries2(i,'miconazole nitrate')
}

```

```{r}
getGeneSummaries('miconazole nitrate')
getGeneSummaries('milk protein isolate')
getGeneSummaries('mineral oil')
getGeneSummaries('monohydrate')
getGeneSummaries('mononucleosis')
getGeneSummaries('mushrooms')
getGeneSummaries('neuroma')
getGeneSummaries('nicotine')
getGeneSummaries('nitric oxide')
getGeneSummaries('norepinephrine')
getGeneSummaries('okra')
getGeneSummaries('onions')
getGeneSummaries('opiates')
getGeneSummaries('orange')
getGeneSummaries('oregano')

```

```{r}
miconazoleNitrateSumms <- read.csv("proteinGeneSummaries_miconazole-nitrate.csv")
milkProteinIsolateSumms <- read.csv("proteinGeneSummaries_milk-protein-isolate.csv")
mineralOilSumms <- read.csv("proteinGeneSummaries_mineral-oil.csv")
monohydrateSumms <- read.csv("proteinGeneSummaries_monohydrate.csv")
mononucleosisSumms <- read.csv("proteinGeneSummaries_mononucleosis.csv")
mushroomsSumms <- read.csv("proteinGeneSummaries_mushrooms.csv")
neuromaSumms <- read.csv("proteinGeneSummaries_neuroma.csv")
nicotineSumms <- read.csv("proteinGeneSummaries_nicotine.csv")
nitricOxideSumms <- read.csv("proteinGeneSummaries_nitric-oxide.csv")
norepinephrineSumms <- read.csv("proteinGeneSummaries_norepinephrine.csv")
okraSumms <- read.csv("proteinGeneSummaries_okra.csv")
onionsSumms <- read.csv("proteinGeneSummaries_onions.csv")
opiatesSumms <- read.csv("proteinGeneSummaries_opiates.csv")
orangeSumms <- read.csv("proteinGeneSummaries_orange.csv")
oreganoSumms <- read.csv("proteinGeneSummaries_oregano.csv")

```




```{r}
for (i in methylparaben$proteinType[1:5]){
  getSummaries2(i,'methylparaben')
}

for (i in meth$proteinType[1:5]){
  getSummaries2(i,'methamphetamines')
}

for (i in mdma$proteinType[1:5]){
  getSummaries2(i,'mdma')
}

for (i in matches$proteinType[1:5]){
  getSummaries2(i,'matches')
}

for (i in mapleSyrup$proteinType[1:5]){
  getSummaries2(i,'maple syrup')
}

for (i in mango$proteinType[1:5]){
  getSummaries2(i,'mango')
}

for (i in malaria$proteinType[1:5]){
  getSummaries2(i,'malaria')
}

for (i in magnesiumCarbonate$proteinType[1:5]){
  getSummaries2(i,'magnesium carbonate')
}

for (i in macadamiaNuts$proteinType[1:3]){
  getSummaries2(i,'macadamia nuts')
}

for (i in lime$proteinType[1:5]){
  getSummaries2(i,'lime')
}

for (i in lentils$proteinType[1:5]){
  getSummaries2(i,'lentils')
}

for (i in lemon$proteinType[1:5]){
  getSummaries2(i,'lemon')
}

for (i in latex$proteinType[1:5]){
  getSummaries2(i,'latex')
}

for (i in ketamine$proteinType[1:5]){
  getSummaries2(i,'ketamine')
}

for (i in kale$proteinType[1:5]){
  getSummaries2(i,'kale')
}

```

```{r}
getGeneSummaries('methylparaben')
getGeneSummaries('methamphetamines')
getGeneSummaries('mdma')
getGeneSummaries('matches')
getGeneSummaries('maple syrup')
getGeneSummaries('mango')
getGeneSummaries('malaria')
getGeneSummaries('magnesium carbonate')
getGeneSummaries('macadamia nuts')
getGeneSummaries('lime')
getGeneSummaries('lentils')
getGeneSummaries('lemon')
getGeneSummaries('latex')
getGeneSummaries('ketamine')
getGeneSummaries('kale')

```

```{r}
methylparabenSumms <- read.csv("proteinGeneSummaries_methylparaben.csv")
methSumms <- read.csv("proteinGeneSummaries_methamphetamines.csv")
mdmaSumms <- read.csv("proteinGeneSummaries_mdma.csv")
matchesSumms <- read.csv("proteinGeneSummaries_matches.csv")
mapleSyrupSumms <- read.csv("proteinGeneSummaries_maple-syrup.csv")
mangoSumms <- read.csv("proteinGeneSummaries_mango.csv")
malariaSumms <- read.csv("proteinGeneSummaries_malaria.csv")
magnesiumCarbonateSumms <- read.csv("proteinGeneSummaries_magnesium-carbonate.csv")
macadamiaNutsSumms <- read.csv("proteinGeneSummaries_macadamia-nuts.csv")
limeSumms <- read.csv("proteinGeneSummaries_lime.csv")
lentilsSumms <- read.csv("proteinGeneSummaries_lentils.csv")
lemonSumms <- read.csv("proteinGeneSummaries_lemon.csv")
latexSumms <- read.csv("proteinGeneSummaries_latex.csv")
ketamineSumms <- read.csv("proteinGeneSummaries_ketamine.csv")
kaleSumms <- read.csv("proteinGeneSummaries_kale.csv")

```


```{r}
for (i in jasmine$proteinType[1:4]){
  getSummaries2(i,'jasmine')
}

for (i in jackfruit$proteinType[1:5]){
  getSummaries2(i,'jackfruit')}

for (i in iud$proteinType[1:5]){
  getSummaries2(i,'intra uterine device')}

for (i in isopropylPalmitate$proteinType[1:5]){
  getSummaries2(i,'isopropyl palmitate')}

for (i in isopropylMyristate$proteinType[1:5]){
  getSummaries2(i,'isopropyl myristate')}

for (i in isobutane$proteinType[1]){
  getSummaries2(i,'isobutane')}

for (i in incontinence$proteinType[1:5]){
  getSummaries2(i,'incontinence')}

for (i in hydroxypropylCellulose$proteinType[1:5]){
  getSummaries2(i,'hydroxypropyl cellulose')}

for (i in hydroxyethylCellulose$proteinType[1:5]){
  getSummaries2(i,'hydroxyethyl cellulose')}

for (i in hydrogenatedPalmOilGlyceride$proteinType[1:5]){
  getSummaries2(i,'hydrogenated palm oil glyceride')}

for (i in hydrogenatedCastorOil$proteinType[1:5]){
  getSummaries2(i,'hydrogenated castor oil')}

for (i in herpes2$proteinType[1:5]){
  getSummaries2(i,'herpes simplex 2')}

for (i in herpes1$proteinType[1:5]){
  getSummaries2(i,'herpes simplex 1')}

for (i in heroin$proteinType[1:5]){
  getSummaries2(i,'heroin')}
  
for (i in hazelnuts$proteinType[1:5]){
  getSummaries2(i,'hazel nuts')}


```

```{r}
getGeneSummaries('hazel nuts')
getGeneSummaries('heroin')
getGeneSummaries('herpes simplex 1')
getGeneSummaries('herpes simplex 2')
getGeneSummaries('hydrogenated castor oil')
getGeneSummaries('hydrogenated palm oil glyceride')
getGeneSummaries('hydroxyethyl cellulose')
getGeneSummaries('hydroxypropyl cellulose')
getGeneSummaries('incontinence')
getGeneSummaries('isobutane')
getGeneSummaries('isopropyl myristate')
getGeneSummaries('isopropyl palmitate')
getGeneSummaries('intra uterine device')
getGeneSummaries('jackfruit')
getGeneSummaries('jasmine')

```


```{r}
hazelnutsSumms <- read.csv("proteinGeneSummaries_hazel-nuts.csv")
heroinSumms <- read.csv("proteinGeneSummaries_heroin.csv")
herpes1Summs <- read.csv("proteinGeneSummaries_herpes-simplex-1.csv")
herpes2Summs <- read.csv("proteinGeneSummaries_herpes-simplex-2.csv")
hydrogenatedCastorOilSumms <- read.csv("proteinGeneSummaries_hydrogenated-castor-oil.csv")
hydrogenatedPalmOilGlycerideSumms <- read.csv("proteinGeneSummaries_hydrogenated-palm-oil-glyceride.csv")
hydroxyethylCelluloseSumms <- read.csv("proteinGeneSummaries_hydroxyethyl-cellulose.csv")
hydroxypropylCelluloseSumms <- read.csv("proteinGeneSummaries_hydroxypropyl-cellulose.csv")
incontinenceSumms <- read.csv("proteinGeneSummaries_incontinence.csv")
isobutaneSumms <- read.csv("proteinGeneSummaries_isobutane.csv")
isopropylMyristateSumms <- read.csv("proteinGeneSummaries_isopropyl-myristate.csv")
isopropylPalmitateSumms <- read.csv("proteinGeneSummaries_isopropyl-palmitate.csv")
iudSumms <- read.csv("proteinGeneSummaries_intra-uterine-device.csv")
jackfruitSumms <- read.csv("proteinGeneSummaries_jackfruit.csv")
jasmineSumms <- read.csv("proteinGeneSummaries_jasmine.csv")

```



```{r}
for (i in gunPowder$proteinType[1:5]){
  getSummaries2(i,'gun powder')}

for (i in greenTea$proteinType[1:5]){
  getSummaries2(i,'green tea')}

for (i in greenOnions$proteinType[1:5]){
  getSummaries2(i,'green onions')}

for (i in greenBeans$proteinType[1:5]){
  getSummaries2(i,'green beans')}

for (i in grapefruit$proteinType[1:5]){
  getSummaries2(i,'grapefruit')}

for (i in gonorrhea$proteinType[1:5]){
  getSummaries2(i,'gonorrhea')}

for (i in goldenseal$proteinType[1:5]){
  getSummaries2(i,'golden seal')}

for (i in glycerine$proteinType[1:5]){
  getSummaries2(i,'glycerine')}

for (i in gluconolactone$proteinType[1:5]){
  getSummaries2(i,'gluconolactone')}

for (i in ginseng$proteinType[1:5]){
  getSummaries2(i,'ginseng')}

for (i in gingkoBiloba$proteinType[1:5]){
  getSummaries2(i,'gingko biloba')}

for (i in ginger$proteinType[1:5]){
  getSummaries2(i,'ginger')}

for (i in ghb$proteinType[1:5]){
  getSummaries2(i,'ghb')}

for (i in gelatin$proteinType[1:5]){
  getSummaries2(i,'gelatin')}

for (i in garlic$proteinType[1:5]){
  getSummaries2(i,'garlic')}

for (i in flavanoids$proteinType[1:5]){
  getSummaries2(i,'flavanoids')}

for (i in figs$proteinType[1:5]){
  getSummaries2(i,'figs')}

```

```{r}
getGeneSummaries('gun powder')
getGeneSummaries('green tea')
getGeneSummaries('green onions')
getGeneSummaries('green beans')
getGeneSummaries('grapefruit')
getGeneSummaries('gonorrhea')
getGeneSummaries('golden seal')
getGeneSummaries('glycerine')
getGeneSummaries('gluconolactone')
getGeneSummaries('ginseng')
getGeneSummaries('gingko biloba')
getGeneSummaries('ginger')
getGeneSummaries('ghb')
getGeneSummaries('gelatin')
getGeneSummaries('garlic')
getGeneSummaries('flavanoids')
getGeneSummaries('figs')

```

```{r}
gunPowderSumms <- read.csv("proteinGeneSummaries_gun-powder.csv")
greenTeaSumms <- read.csv("proteinGeneSummaries_green-tea.csv")
greenOnionsSumms <- read.csv("proteinGeneSummaries_green-onions.csv")
greenBeansSumms <- read.csv("proteinGeneSummaries_green-beans.csv")
grapefruitSumms <- read.csv("proteinGeneSummaries_grapefruit.csv")
gonorrheaSumms <- read.csv("proteinGeneSummaries_gonorrhea.csv")
goldensealSumms <- read.csv("proteinGeneSummaries_golden-seal.csv")
glycerineSumms <- read.csv("proteinGeneSummaries_glycerine.csv")
gluconolactoneSumms <- read.csv("proteinGeneSummaries_gluconolactone.csv")
ginsengSumms <- read.csv("proteinGeneSummaries_ginseng.csv")
gingkoBilobaSumms <- read.csv("proteinGeneSummaries_gingko-biloba.csv")
gingerSumms <- read.csv("proteinGeneSummaries_ginger.csv")
ghbSumms <- read.csv("proteinGeneSummaries_ghb.csv")
gelatinSumms <- read.csv("proteinGeneSummaries_gelatin.csv")
garlicSumms <- read.csv("proteinGeneSummaries_garlic.csv")
flavanoidsSumms <- read.csv("proteinGeneSummaries_flavanoids.csv")
figsSumms <- read.csv("proteinGeneSummaries_figs.csv")

```



```{r}
for (i in fibromyalgia$proteinType[1:5]){
  getSummaries2(i,'fibromyalgia')}

for (i in fennel$proteinType[1:5]){
  getSummaries2(i,'fennel')}

for (i in eucalyptus$proteinType[1:5]){
  getSummaries2(i,'eucalyptus')}

for (i in ethanol$proteinType[1:5]){
  getSummaries2(i,'ethanol')}

for (i in epsteinBarr$proteinType[1:5]){
  getSummaries2(i,'epstein barr virus')}

for (i in epinephrine$proteinType[1:5]){
  getSummaries2(i,'epinephrine')}

for (i in eggPlant$proteinType[1:5]){
  getSummaries2(i,'egg plant')}

for (i in echinacea$proteinType[1:5]){
  getSummaries2(i,'echinacea')}

for (i in dmaa$proteinType[1:5]){
  getSummaries2(i,'dmaa')}

for (i in dextrin$proteinType[1:5]){
  getSummaries2(i,'dextrin')}

for (i in depression$proteinType[1:5]){
  getSummaries2(i,'depression')}

for (i in demerol$proteinType[1:5]){
  getSummaries2(i,'demerol')}

for (i in deet$proteinType[1:5]){
  getSummaries2(i,'deet')}

for (i in dates$proteinType[1:5]){
  getSummaries2(i,'dates')}

for (i in curry$proteinType[1:5]){
  getSummaries2(i,'curry')}

for (i in crying$proteinType[1:5]){
  getSummaries2(i,'crying')}

```


```{r}
getGeneSummaries('fibromyalgia')
getGeneSummaries('fennel')
getGeneSummaries('eucalyptus')
getGeneSummaries('ethanol')
getGeneSummaries('epstein barr virus')
getGeneSummaries('epinephrine')
getGeneSummaries('egg plant')
getGeneSummaries('echinacea')
getGeneSummaries('dmaa')
getGeneSummaries('dextrin')
getGeneSummaries('depression')
getGeneSummaries('demerol')
getGeneSummaries('deet')
getGeneSummaries('dates')
getGeneSummaries('curry')
getGeneSummaries('crying')


```


```{r}
fibromyalgiaSumms <- read.csv("proteinGeneSummaries_fibromyalgia.csv")
fennelSumms <- read.csv("proteinGeneSummaries_fennel.csv")
eucalyptusSumms <- read.csv("proteinGeneSummaries_eucalyptus.csv")
ethanolSumms <- read.csv("proteinGeneSummaries_ethanol.csv")
epsteinBarrSumms <- read.csv("proteinGeneSummaries_epstein-barr-virus.csv")
epinephrineSumms <- read.csv("proteinGeneSummaries_epinephrine.csv")
eggPlantSumms <- read.csv("proteinGeneSummaries_egg-plant.csv")
echinaceaSumms <- read.csv("proteinGeneSummaries_echinacea.csv")
dmaaSumms <- read.csv("proteinGeneSummaries_dmaa.csv")
dextrinSumms <- read.csv("proteinGeneSummaries_dextrin.csv")
depressionSumms <- read.csv("proteinGeneSummaries_depression.csv")
demerolSumms <- read.csv("proteinGeneSummaries_demerol.csv")
deetSumms <- read.csv("proteinGeneSummaries_deet.csv")
datesSumms <- read.csv("proteinGeneSummaries_dates.csv")
currySumms <- read.csv("proteinGeneSummaries_curry.csv")
cryingSumms <- read.csv("proteinGeneSummaries_crying.csv")

```


```{r}
for (i in cranberries$proteinType[1:5]){
  getSummaries2(i,'cranberries')}

for (i in cotton$proteinType[1:5]){
  getSummaries2(i,'cotton')}

for (i in cornStarch$proteinType[1:5]){
  getSummaries2(i,'corn starch')}

for (i in cornNuts$proteinType[1:5]){
  getSummaries2(i,'corn nuts')}

for (i in corn$proteinType[1:5]){
  getSummaries2(i,'corn')}

for (i in codeine$proteinType[1:5]){
  getSummaries2(i,'codeine')}

for (i in coconuts$proteinType[1:5]){
  getSummaries2(i,'coconuts')}

for (i in cocaine$proteinType[1:5]){
  getSummaries2(i,'cocaine')}

for (i in claritin$proteinType[1:5]){
  getSummaries2(i,'claritin')}

for (i in chocolate$proteinType[1:5]){
  getSummaries2(i,'chocolate')}

for (i in chlorhexidineGluconate$proteinType[1:5]){
  getSummaries2(i,'chlorhexidine gluconate')}

for (i in chlamydia$proteinType[1:5]){
  getSummaries2(i,'chlamydia')}

for (i in chestnuts$proteinType[1:5]){
  getSummaries2(i,'chestnuts')}

for (i in cherries$proteinType[1:5]){
  getSummaries2(i,'cherries')}

for (i in chamomile$proteinType[1:5]){
  getSummaries2(i,'chamomile')}

```


```{r}
getGeneSummaries('chamomile')
getGeneSummaries('cherries')
getGeneSummaries('chestnuts')
getGeneSummaries('chlamydia')
getGeneSummaries('chlorhexidine gluconate')
getGeneSummaries('chocolate')
getGeneSummaries('claritin')
getGeneSummaries('cocaine')
getGeneSummaries('coconuts')
getGeneSummaries('codeine')
getGeneSummaries('corn')
getGeneSummaries('corn nuts')
getGeneSummaries('corn starch')
getGeneSummaries('cotton')
getGeneSummaries('cranberries')

```


```{r}
chamomileSumms <- read.csv("proteinGeneSummaries_chamomile.csv")
cherriesSumms <- read.csv("proteinGeneSummaries_cherries.csv")
chestnutsSumms <- read.csv("proteinGeneSummaries_chestnuts.csv")
chlamydiaSumms <- read.csv("proteinGeneSummaries_chlamydia.csv")
chlorhexidineGluconateSumms <- read.csv("proteinGeneSummaries_chlorhexidine-gluconate.csv")
chocolateSumms <- read.csv("proteinGeneSummaries_chocolate.csv")
claritinSumms <- read.csv("proteinGeneSummaries_claritin.csv")
cocaineSumms <- read.csv("proteinGeneSummaries_cocaine.csv")
coconutsSumms <- read.csv("proteinGeneSummaries_coconuts.csv")
codeineSumms <- read.csv("proteinGeneSummaries_codeine.csv")
cornSumms <- read.csv("proteinGeneSummaries_corn.csv")
cornNutsSumms <- read.csv("proteinGeneSummaries_corn-nuts.csv")
cornStarchSumms <- read.csv("proteinGeneSummaries_corn-starch.csv")
cottonSumms <- read.csv("proteinGeneSummaries_cotton.csv")
cranberriesSumms <- read.csv("proteinGeneSummaries_cranberries.csv")

```




```{r}
for (i in celery$proteinType[1:5]){
  getSummaries2(i,'celery')}

for (i in cashews$proteinType[1:5]){
  getSummaries2(i,'cashews')}

for (i in carrots$proteinType[1:5]){
  getSummaries2(i,'carrots')}

for (i in carrageenan$proteinType[1:5]){
  getSummaries2(i,'carrageenan')}

for (i in caraway$proteinType[1:2]){
  getSummaries2(i,'caraway')}

for (i in candles$proteinType[1:5]){
  getSummaries2(i,'candles')}

for (i in cabbage$proteinType[1:5]){
  getSummaries2(i,'cabbage')}

for (i in butane$proteinType[1:5]){
  getSummaries2(i,'butane')}

for (i in bugSpray$proteinType[1:5]){
  getSummaries2(i,'bug spray')}

for (i in broccoliSprouts$proteinType[1:5]){
  getSummaries2(i,'broccoli sprouts')}

for (i in broccoli$proteinType[1:5]){
  getSummaries2(i,'broccoli')}

for (i in brazilNuts$proteinType[1:5]){
  getSummaries2(i,'brazil nuts')}

for (i in bocChoi$proteinType[1:5]){
  getSummaries2(i,'boc choi')}

for (i in blueberries$proteinType[1:5]){
  getSummaries2(i,'blueberries')}

for (i in blackEyedPeas$proteinType[1:5]){
  getSummaries2(i,'black eyed peas')}


```


```{r}
getGeneSummaries('celery')
getGeneSummaries('cashews')
getGeneSummaries('carrots')
getGeneSummaries('carrageenan')
getGeneSummaries('caraway')
getGeneSummaries('candles')
getGeneSummaries('cabbage')
getGeneSummaries('butane')
getGeneSummaries('bug spray')
getGeneSummaries('broccoli sprouts')
getGeneSummaries('broccoli')
getGeneSummaries('brazil nuts')
getGeneSummaries('boc choi')
getGeneSummaries('blueberries')
getGeneSummaries('black eyed peas')


```

```{r}
celerySumms <- read.csv("proteinGeneSummaries_celery.csv")
cashewsSumms <- read.csv("proteinGeneSummaries_cashews.csv")
carrotsSumms <- read.csv("proteinGeneSummaries_carrots.csv")
carrageenanSumms <- read.csv("proteinGeneSummaries_carrageenan.csv")
carawaySumms <- read.csv("proteinGeneSummaries_caraway.csv")
candlesSumms <- read.csv("proteinGeneSummaries_candles.csv")
cabbageSumms <- read.csv("proteinGeneSummaries_cabbage.csv")
butaneSumms <- read.csv("proteinGeneSummaries_butane.csv")
bugSpraySumms <- read.csv("proteinGeneSummaries_bug-spray.csv")
broccoliSproutsSumms <- read.csv("proteinGeneSummaries_broccoli-sprouts.csv")
broccoliSumms <- read.csv("proteinGeneSummaries_broccoli.csv")
brazilNutsSumms <- read.csv("proteinGeneSummaries_brazil-nuts.csv")
bocChoiSumms <- read.csv("proteinGeneSummaries_boc-choi.csv")
blueberriesSumms <- read.csv("proteinGeneSummaries_blueberries.csv")
blackEyedPeasSumms <- read.csv("proteinGeneSummaries_black-eyed-peas.csv")


```



```{r}
for (i in blackberries$proteinType[1:5]){
  getSummaries2(i,'blackberries')}

for (i in birthContraceptive$proteinType[1:5]){
  getSummaries2(i,'birth contraceptive')}

for (i in bht$proteinType[1:5]){
  getSummaries2(i,'bht')}

for (i in betaineAnhydrous$proteinType[1:5]){
  getSummaries2(i,'betaine anhydrous')}

for (i in betaAlanine$proteinType[1:5]){
  getSummaries2(i,'beta alanine')}

for (i in benadryl$proteinType[1:5]){
  getSummaries2(i,'benadryl')}

for (i in beets$proteinType[1:5]){
  getSummaries2(i,'beets')}

for (i in beanSprouts$proteinType[1:5]){
  getSummaries2(i,'bean sprouts')}

for (i in beans$proteinType[1:5]){
  getSummaries2(i,'beans')}

for (i in bayLeaves$proteinType[1:5]){
  getSummaries2(i,'bay leaves')}

for (i in basil$proteinType[1:5]){
  getSummaries2(i,'basil')}

for (i in bananas$proteinType[1:5]){
  getSummaries2(i,'bananas')}

for (i in babyPowder$proteinType[1:5]){
  getSummaries2(i,'baby powder')}

for (i in arugula$proteinType[1]){
  getSummaries2(i,'arugula')}

for (i in anxiety$proteinType[1:5]){
  getSummaries2(i,'anxiety')}


```

```{r}
getGeneSummaries('blackberries')
getGeneSummaries('birth contraceptive')
getGeneSummaries('bht')
getGeneSummaries('betaine anhydrous')
getGeneSummaries('beta alanine')
getGeneSummaries('benadryl')
getGeneSummaries('beets')
getGeneSummaries('bean sprouts')
getGeneSummaries('beans')
getGeneSummaries('bay leaves')
getGeneSummaries('basil')
getGeneSummaries('bananas')
getGeneSummaries('baby powder')
getGeneSummaries('arugula')
getGeneSummaries('anxiety')

```

```{r}
blackberriesSumms <- read.csv("proteinGeneSummaries_blackberries.csv")
birthContraceptiveSumms <- read.csv("proteinGeneSummaries_birth-contraceptive.csv")
bhtSumms <- read.csv("proteinGeneSummaries_bht.csv")
betaineAnhydrousSumms <- read.csv("proteinGeneSummaries_betaine-anhydrous.csv")
betaAlanineSumms <- read.csv("proteinGeneSummaries_beta-alanine.csv")
benadrylSumms <- read.csv("proteinGeneSummaries_benadryl.csv")
beetsSumms <- read.csv("proteinGeneSummaries_beets.csv")
beanSproutsSumms <- read.csv("proteinGeneSummaries_bean-sprouts.csv")
beansSumms <- read.csv("proteinGeneSummaries_beans.csv")
bayLeavesSumms <- read.csv("proteinGeneSummaries_bay-leaves.csv")
basilSumms <- read.csv("proteinGeneSummaries_basil.csv")
bananasSumms <- read.csv("proteinGeneSummaries_bananas.csv")
babyPowderSumms <- read.csv("proteinGeneSummaries_baby-powder.csv")
arugulaSumms <- read.csv("proteinGeneSummaries_arugula.csv")
anxietySumms <- read.csv("proteinGeneSummaries_anxiety.csv")

```



```{r}
for (i in antipsychotics$proteinType[1:5]){
  getSummaries2(i,'antipsychotics')}

for (i in antihistamine$proteinType[1:5]){
  getSummaries2(i,'antihistamine')}

for (i in anise$proteinType[1:5]){
  getSummaries2(i,'anise')}

for (i in anesthesia$proteinType[1:5]){
  getSummaries2(i,'anesthesia')}

for (i in aminomethylPropanol$proteinType[1:5]){
  getSummaries2(i,'aminomethyl propanol')}

for (i in almonds$proteinType[1:5]){
  getSummaries2(i,'almonds')}

for (i in allylPentaerythritolCrosslinked$proteinType[1:4]){
  getSummaries2(i,'allyl pentaerythritol crosslinked')}

for (i in allegra$proteinType[1:5]){
  getSummaries2(i,'allegra')}

for (i in adaptogenBlend$proteinType[1]){
  getSummaries2(i,'adaptogen blend')}

for (i in acetylcholine$proteinType[1:5]){
  getSummaries2(i,'acetylcholine')}

for (i in acesulfamePotassium$proteinType[1:4]){
  getSummaries2(i,'acesulfame potassium')}


```

```{r}
find25genes('bacon')
find25genes('cialis')
find25genes('viagra')
find25genes('erectile disfunction')
find25genes('oysters')
```

```{r}
getProteinGenes('bacon')
getProteinGenes('cialis')
getProteinGenes('viagra')
getProteinGenes('erectile disfunction')
getProteinGenes('oysters')
```

```{r}
bacon <- read.csv("Top25bacons.csv")
cialis <- read.csv("Top25cialiss.csv")
viagra <- read.csv("Top25viagras.csv")
erectileDisfunction <- read.csv("Top25erectile-disfunctions.csv")
oysters <- read.csv('Top25oysterss.csv')
```

```{r}
for (i in bacon$proteinType[1:5]){
  getSummaries2(i,'bacon')
}

for (i in cialis$proteinType[1:5]){
  getSummaries2(i,'cialis')
}

for (i in viagra$proteinType[1:5]){
  getSummaries2(i,'viagra')
}

for (i in erectileDisfunction$proteinType[1:5]){
  getSummaries2(i,'erectile disfunction')
}

for (i in oysters$proteinType[1:5]){
  getSummaries2(i,'oysters')
}
```



```{r}
getGeneSummaries('antipsychotics')
getGeneSummaries('antihistamine')
getGeneSummaries('anise')
getGeneSummaries('anesthesia')
getGeneSummaries('aminomethyl propanol')
getGeneSummaries('almonds')
getGeneSummaries('allyl pentaerythritol crosslinked')
getGeneSummaries('allegra')
getGeneSummaries('adaptogen blend')
getGeneSummaries('acetylcholine')
getGeneSummaries('acesulfame potassium')
getGeneSummaries('bacon')
getGeneSummaries('cialis')
getGeneSummaries('viagra')
getGeneSummaries('erectile disfunction')
getGeneSummaries('oysters')


```

```{r}
antipsychoticsSumms <- read.csv("proteinGeneSummaries_antipsychotics.csv")
antihistamineSumms <- read.csv("proteinGeneSummaries_antihistamine.csv")
aniseSumms <- read.csv("proteinGeneSummaries_anise.csv")
anesthesiaSumms <- read.csv("proteinGeneSummaries_anesthesia.csv")
aminomethylPropanolSumms <- read.csv("proteinGeneSummaries_aminomethyl-propanol.csv")
almondsSumms <- read.csv("proteinGeneSummaries_almonds.csv")
allylPentaerythritolCrosslinkedSumms <- read.csv("proteinGeneSummaries_allyl-pentaerythritol-crosslinked.csv")
allegraSumms <- read.csv("proteinGeneSummaries_allegra.csv")
adaptogenBlendSumms <- read.csv("proteinGeneSummaries_adaptogen-blend.csv")
acetycholineSumms <- read.csv("proteinGeneSummaries_acetylcholine.csv")
acesulfamePotassiumSumms <- read.csv("proteinGeneSummaries_acesulfame-potassium.csv")
baconSumms <- read.csv("proteinGeneSummaries_bacon.csv")
cialisSumms <- read.csv("proteinGeneSummaries_cialis.csv")
viagraSumms <- read.csv("proteinGeneSummaries_viagra.csv")
erectileDisfunctionSumms <- read.csv("proteinGeneSummaries_erectile-disfunction.csv")
oystersSumms <- read.csv("proteinGeneSummaries_oysters.csv")

```

```{r}
newSystems <- rbind(antipsychoticsSumms, 
antihistamineSumms ,
aniseSumms ,
anesthesiaSumms, 
aminomethylPropanolSumms ,
almondsSumms ,
allylPentaerythritolCrosslinkedSumms, 
allegraSumms ,
adaptogenBlendSumms ,
acetycholineSumms ,
acesulfamePotassiumSumms ,
baconSumms ,
cialisSumms ,
viagraSumms ,
erectileDisfunctionSumms ,
oystersSumms ,
blackberriesSumms ,
birthContraceptiveSumms ,
bhtSumms ,
betaineAnhydrousSumms ,
betaAlanineSumms ,
benadrylSumms ,
beetsSumms ,
beanSproutsSumms ,
beansSumms ,
bayLeavesSumms ,
basilSumms ,
bananasSumms, 
babyPowderSumms ,
arugulaSumms ,
anxietySumms ,
celerySumms ,
cashewsSumms ,
carrotsSumms ,
carrageenanSumms ,
carawaySumms ,
candlesSumms ,
cabbageSumms ,
butaneSumms ,
bugSpraySumms, 
broccoliSproutsSumms ,
broccoliSumms ,
brazilNutsSumms, 
bocChoiSumms ,
blueberriesSumms ,
blackEyedPeasSumms, 
chamomileSumms ,
cherriesSumms ,
chestnutsSumms ,
chlamydiaSumms ,
chlorhexidineGluconateSumms ,
chocolateSumms ,
claritinSumms ,
cocaineSumms ,
coconutsSumms ,
codeineSumms ,
cornSumms ,
cornNutsSumms ,
cornStarchSumms, 
cottonSumms ,
cranberriesSumms ,
fibromyalgiaSumms ,
fennelSumms ,
eucalyptusSumms ,
ethanolSumms ,
epsteinBarrSumms ,
epinephrineSumms ,
eggPlantSumms ,
echinaceaSumms ,
dmaaSumms ,
dextrinSumms ,
depressionSumms ,
demerolSumms ,
deetSumms ,
datesSumms ,
currySumms ,
cryingSumms ,
gunPowderSumms, 
greenTeaSumms ,
greenOnionsSumms ,
greenBeansSumms ,
grapefruitSumms ,
gonorrheaSumms ,
goldensealSumms ,
glycerineSumms ,
gluconolactoneSumms ,
ginsengSumms ,
gingkoBilobaSumms ,
gingerSumms ,
ghbSumms ,
gelatinSumms ,
garlicSumms ,
flavanoidsSumms ,
figsSumms ,
hazelnutsSumms ,
heroinSumms ,
herpes1Summs ,
herpes2Summs ,
hydrogenatedCastorOilSumms ,
hydrogenatedPalmOilGlycerideSumms ,
hydroxyethylCelluloseSumms ,
hydroxypropylCelluloseSumms ,
incontinenceSumms ,
isobutaneSumms ,
isopropylMyristateSumms ,
isopropylPalmitateSumms ,
iudSumms ,
jackfruitSumms ,
jasmineSumms ,
methylparabenSumms ,
methSumms ,
mdmaSumms ,
matchesSumms ,
mapleSyrupSumms ,
mangoSumms ,
malariaSumms, 
magnesiumCarbonateSumms ,
macadamiaNutsSumms ,
limeSumms ,
lentilsSumms ,
lemonSumms ,
latexSumms ,
ketamineSumms ,
kaleSumms ,
miconazoleNitrateSumms ,
milkProteinIsolateSumms ,
mineralOilSumms ,
monohydrateSumms ,
mononucleosisSumms, 
mushroomsSumms ,
neuromaSumms ,
nicotineSumms ,
nitricOxideSumms ,
norepinephrineSumms ,
okraSumms ,
onionsSumms, 
opiatesSumms, 
orangeSumms ,
oreganoSumms ,
polycarbophilSumms ,
plumsSumms ,
pistachioSumms ,
pineNutsSumms ,
pineappleSumms ,
perfumeSumms ,
pepperSpraySumms ,
peppersSumms ,
peppercornSumms ,
peg8Summs ,
pecansSumms, 
peasSumms ,
peanutsSumms ,
parfumSumms ,
papayaSeedsSumms ,
papayaSumms ,
polyesterSumms ,
polyethyleneSumms ,
polypropyleneSumms, 
polyurethaneSumms ,
propaneSumms ,
propyleneGlycolSumms ,
psychedelicSumms ,
pumpkinSumms ,
rayonSumms ,
redFennelSumms ,
redOnionsSumms ,
rohypnolSumms ,
rosemarySumms ,
salmonSumms ,
schisandraChinensisSumms ,
sudafedSumms ,
sucraloseSumms, 
strawberriesSumms ,
stJohnsWartSumms, 
stearylAlcoholSumms ,
starFruitSumms ,
squashSumms ,
spermicideSumms ,
soyLecithinSumms ,
soySumms ,
sodiumHydroxideSumms ,
sodiumBenzoateSumms ,
siliconeSumms ,
shinglesSumms ,
sexLubricantSumms ,
sesameSeedsSumms ,
sunflowerSeedsSumms ,
sweetPotatoSumms ,
syphilisSumms ,
talcSumms ,
tanninsSumms ,
tearGasSumms ,
tuberculosisSumms ,
turmericSumms ,
turnipGreensSumms ,
tylenolPMSumms ,
vaginalDrynessSumms ,
vicodineSumms ,
visineSumms ,
walnutsSumms ,
watermelonSumms ,
weedEaterSumms ,
weedKillerSumms ,
wheyProteinIsolateSumms ,
xanaxSumms ,
yamsSumms ,
yeastInfectionSumms ,
yerbaMateSumms ,
yohimbeSumms ,
zucchiniSumms 
)
colnames(newSystems)
```

```{r}
previousBodySystems1 <- read.csv('bodySystems3.csv')
colnames(previousBodySystems1)
```


```{r}
newSystems2 <- newSystems[,c(2,1,3:5,6)]
previousBodySystems <- previousBodySystems1[,c(1:6)]

newSystems3 <- newSystems2[!duplicated(newSystems2),]
```


```{r}
currentBodySystems <- rbind(previousBodySystems,
                            newSystems3)
```

```{r}
write.csv(currentBodySystems,'bodySystems4.csv',row.names = F)
```

```{r}
bs4 <- read.csv('bodySystems4.csv',sep=',',header=T,
                na.strings=c('',' ','NA'),
                stringsAsFactors = T)
```

Add more systems and networks of genes.
```{r}
find25genes('maca root')#vegetable root
find25genes('preparation H')
find25genes('cayenne pepper')
find25genes('shell fish')
find25genes('mercury')
```

```{r}
getProteinGenes('maca root')
getProteinGenes('preparation H')
getProteinGenes('cayenne pepper')
getProteinGenes('shell fish')
getProteinGenes('mercury')
```

```{r}
maca <- read.csv("Top25maca-roots.csv")
prepH <- read.csv("Top25preparation-hs.csv")
cayennePepper <- read.csv("Top25cayenne-peppers.csv")
shellFish <- read.csv("Top25shell-fishs.csv")
mercury <- read.csv("Top25mercurys.csv")
```

```{r}
for (i in maca$proteinType[1:5]){
  getSummaries2(i,'maca')
}

for (i in prepH$proteinType[1:10]){
  getSummaries2(i,'preparation H')
}

for (i in cayennePepper$proteinType[1:3]){
  getSummaries2(i,'cayenne pepper')
}

for (i in shellFish$proteinType[1:10]){
  getSummaries2(i,'shell fish')
}

for (i in mercury$proteinType[1:10]){
  getSummaries2(i,'mercury')
}

```


```{r}
getGeneSummaries('maca')
getGeneSummaries('preparation H')
getGeneSummaries('cayenne pepper')
getGeneSummaries('shell fish')
getGeneSummaries('mercury')

```


```{r}
macaSumms <- read.csv("proteinGeneSummaries_maca.csv")
prepHSumms <- read.csv("proteinGeneSummaries_preparation-h.csv")
cayennePepperSumms <- read.csv("proteinGeneSummaries_cayenne-pepper.csv")
shellFishSumms <- read.csv("proteinGeneSummaries_shell-fish.csv")
mercurySumms <- read.csv("proteinGeneSummaries_mercury.csv")


```


```{r}
newer <- rbind(macaSumms, prepHSumms,cayennePepperSumms,
               shellFishSumms,mercurySumms)
```


```{r}
newer2 <- newer[!duplicated(newer),]
colnames(newer2)
colnames(bs4)
```


```{r}
newer3 <- newer2[,c(2,1,4:6,3)]
```


```{r}
bs5 <- rbind(newer3,bs4)
```


```{r}
write.csv(bs5,'bodySystems5.csv',row.names=F)
```


```{r}
bs5 <- read.csv('bodySystems5.csv',sep=',',
                header=T, na.strings=c('',' ','NA'))

```


```{r}
source('geneCards2.R')
```


```{r}
find25genes('zofran') #treat nausea
find25genes('zantac') #treat stomach acide
find25genes('antiemetics')  #treat nausea
find25genes('antacids') #treat indigestion
find25genes('antipyretics')  #fever reducer
find25genes('sedatives')
find25genes('valium') #treat anxiety
find25genes('soma') #muscle relaxer that blocks pain bw brain and nerves
find25genes('hpv') #human papilloma virus
find25genes('blood thinners') #treat DVT or PE
find25genes('beta blockers') #treat high blood pressure and heart arythmia
```

```{r}
getProteinGenes('zofran')
getProteinGenes('zantac')
getProteinGenes('antiemetics')
getProteinGenes('antacids')
getProteinGenes('sedatives')
getProteinGenes('valium')
getProteinGenes('soma')
getProteinGenes('hpv')
getProteinGenes('blood thinners')
getProteinGenes('beta blockers')
getProteinGenes('antipyretics')


```

```{r}
zofran <- read.csv("Top25zofrans.csv")
zantac <- read.csv("Top25zantacs.csv")
antiemetics <- read.csv("Top25antiemeticss.csv")
antacids <- read.csv("Top25antacidss.csv")
sedatives <- read.csv("Top25sedativess.csv")
valium <- read.csv("Top25valiums.csv")
soma <- read.csv("Top25somas.csv")
hpv <- read.csv("Top25hpvs.csv")
bloodThinners <- read.csv("Top25blood-thinnerss.csv")
betaBlockers <- read.csv("Top25beta-blockerss.csv")
antipyretics <- read.csv("Top25antipyreticss.csv")


```

```{r}
for (i in zofran$proteinType[1:5]){
  getSummaries2(i,'zofran')
}
for (i in zantac$proteinType[1:5]){
  getSummaries2(i,'zantac')
}
for (i in valium$proteinType[1:5]){
  getSummaries2(i,'valium')
}
for (i in soma$proteinType[1:5]){
  getSummaries2(i,'soma')
}
for (i in sedatives$proteinType[1:5]){
  getSummaries2(i,'sedatives')
}
for (i in hpv$proteinType[1:5]){
  getSummaries2(i,'hpv')
}
for (i in bloodThinners$proteinType[1:5]){
  getSummaries2(i,'blood thinners')
}
for (i in betaBlockers$proteinType[1:5]){
  getSummaries2(i,'beta blockers')
}
for (i in antipyretics$proteinType[1:5]){
  getSummaries2(i,'antipyretics')
}
for (i in antiemetics$proteinType[1:5]){
  getSummaries2(i,'antiemetics')
}
for (i in antacids$proteinType[1:5]){
  getSummaries2(i,'antacids')
}

```

```{r}
getGeneSummaries('zofran')
getGeneSummaries('antiemetics')
getGeneSummaries('antipyretics')
getGeneSummaries('beta blockers')
getGeneSummaries('blood thinners')
getGeneSummaries('hpv')
getGeneSummaries('sedatives')
getGeneSummaries('soma')
getGeneSummaries('valium')
getGeneSummaries('zantac')
getGeneSummaries('zofran')
```

```{r}
zofranSumms <- read.csv("proteinGeneSummaries_zofran.csv")
antiemeticsSumms <- read.csv("proteinGeneSummaries_antiemetics.csv")
antipyreticsSumms <- read.csv("proteinGeneSummaries_antipyretics.csv")
betaBlockersSumms <- read.csv("proteinGeneSummaries_beta-blockers.csv")
bloodThinnersSumms <- read.csv("proteinGeneSummaries_blood-thinners.csv")
hpvSumms <- read.csv("proteinGeneSummaries_hpv.csv")
sedativesSumms <- read.csv("proteinGeneSummaries_sedatives.csv")
somaSumms <- read.csv("proteinGeneSummaries_soma.csv")
valiumSumms <- read.csv("proteinGeneSummaries_valium.csv")
zantacSumms <- read.csv("proteinGeneSummaries_zantac.csv")
zofranSumms <- read.csv("proteinGeneSummaries_zofran.csv")


```

```{r}
summs <- rbind(zofranSumms, antiemeticsSumms, antipyreticsSumms,
               betaBlockersSumms,bloodThinnersSumms,hpvSumms,
               sedativesSumms,somaSumms,valiumSumms,zantacSumms,
               zofranSumms)
```


```{r}
colnames(bs5)
colnames(summs)
```

```{r}
summs1 <- summs[,c(2,1,4:6,3)]

bs6 <- rbind(summs1,bs5)

write.csv(bs6,'bodySystems6.csv',row.names=F)
```

Add saffron, an herb for teas and blood boosting immunity.
```{r}
find25genes('saffron')
getProteinGenes('saffron')

```

```{r}
saffron <- read.csv('Top25saffrons.csv')
for (i in saffron$proteinType[1:5]){
  getSummaries2(i,'saffron')
}
getGeneSummaries('saffron')
saffronSumms <- read.csv("proteinGeneSummaries_saffron.csv")
colnames(saffronSumms)
saffronSumms2 <- saffronSumms[,c(2,1,4:6,3)]
colnames(bs6) <- colnames(saffronSumms2)
bs7 <- rbind(saffronSumms2,bs6)
write.csv(bs7,'bodySystems7.csv',row.names=F)
```

```{r}
bs7 <- read.csv('bodySystems7.csv',sep=',',header=T,
                na.strings=c('',' ','NA'))
            
```


```{r}
find25genes('chick peas')
getProteinGenes('chick peas')

chickPeas <- read.csv('Top25chick-peass.csv')
for (i in chickPeas$proteinType[1:5]){
  getSummaries2(i,'chick peas')
}
getGeneSummaries('chick peas')
chickPeasSumms <- read.csv("proteinGeneSummaries_chick-peas.csv")
colnames(chickPeasSumms)
chickPeasSumms2 <- chickPeasSumms[,c(2,1,4:6,3)]


find25genes('antiangiogenics')
getProteinGenes('antiangiogenics')

antiangiogenics <- read.csv('Top25antiangiogenicss.csv')
for (i in antiangiogenics$proteinType[1:5]){
  getSummaries2(i,'antiangiogenics')
}
getGeneSummaries('antiangiogenics')
antiangiogenicsSumms <- read.csv("proteinGeneSummaries_antiangiogenics.csv")
colnames(antiangiogenicsSumms)
antiangiogenicsSumms2 <- antiangiogenicsSumms[,c(2,1,4:6,3)]


find25genes('avocado')
getProteinGenes('avocado')

avocado <- read.csv('Top25avocados.csv')
for (i in avocado$proteinType[1:5]){
  getSummaries2(i,'avocado')
}
getGeneSummaries('avocado')
avocadoSumms <- read.csv("proteinGeneSummaries_avocado.csv")
colnames(avocadoSumms)
avocadoSumms2 <- avocadoSumms[,c(2,1,4:6,3)]




```

```{r}
colnames(bs7) <- colnames(chickPeasSumms2)
bs8 <- rbind(chickPeasSumms2,avocadoSumms2,antiangiogenicsSumms2, bs7)
write.csv(bs8,'bodySystems8.csv',row.names=F)
```

